Illustrating Model Properties

### 2024-06-04 model.qmd
change labels, linestyle

for i, t_stage in enumerate(["early", "late"]):
  axes[i,0].set_ylabel(f"{t_stage} T-cat.", fontweight="bold")
  for j, midext in enumerate([False, True]):
    axes[0,j].set_title("Mid. ext." if midext else "Lateralized", fontweight="bold")
    axes[0,j].set_xticks([])
    axes[-1,j].set_xlabel("prevalence [%]")
    axes[i,j].set_yticks([])
    content = []
    for ipsi, color in zip(
      [{"I": False, "II": False, "III": False, "IV": False, "V": False}, {"III": True}],
      [COLORS["blue"], COLORS["orange"]],
    ):
      scenario = Scenario(
        t_stages=[t_stage],
        midext=midext,
        diagnosis={
          "ipsi": {"max_llh": ipsi},
          "contra": {"max_llh": {"II": True}},
        }
      )
      content.append(
        Histogram.from_hdf5(
          filename=paths.model_dir / "full" / "prevalences_with_ipsi.hdf5",
          dataname=scenario.md5_hash("prevalences"),
          color=color,
          label="prediction",
        )
      )
      content.append(
        BetaPosterior.from_hdf5(
          filename=paths.model_dir / "full" / "prevalences_with_ipsi.hdf5",
          dataname=scenario.md5_hash("prevalences"),
          color=color,
          label="beta",
        )
      )
      num_success, num_total = compute_possible_observed_prevalences(data, scenario).T
      content.append(
          SummedBetaPosterior(
          num_success=num_success,
          num_total=num_total,
          kwargs={"linestyle": "--"},
        )
      )
    draw(
      axes=axes[i,j],
      contents=content,
      xlims=(0., 30. if midext else 10.),
    )

>>>>

for i, t_stage in enumerate(["early", "late"]):
  axes[i,0].set_ylabel(f"{t_stage} T-cat.", fontweight="bold")
  for j, midext in enumerate([False, True]):
    axes[0,j].set_title("Mid. ext." if midext else "Lateralized", fontweight="bold")
    axes[0,j].set_xticks([])
    axes[-1,j].set_xlabel("prevalence [%]")
    axes[i,j].set_yticks([])
    content = []
    for ipsi, color in zip(
      [{"I": False, "II": False, "III": False, "IV": False, "V": False}, {"III": True}],
      [COLORS["blue"], COLORS["orange"]],
    ):
      scenario = Scenario(
        t_stages=[t_stage],
        midext=midext,
        diagnosis={
          "ipsi": {"max_llh": ipsi},
          "contra": {"max_llh": {"II": True}},
        }
      )
      content.append(
        Histogram.from_hdf5(
          filename=paths.model_dir / "full" / "prevalences_with_ipsi.hdf5",
          dataname=scenario.md5_hash("prevalences"),
          color=color,
          label="prediction",
        )
      )
      content.append(
        BetaPosterior.from_hdf5(
          filename=paths.model_dir / "full" / "prevalences_with_ipsi.hdf5",
          dataname=scenario.md5_hash("prevalences"),
          color=color,
        )
      )
      num_success, num_total = compute_possible_observed_prevalences(data, scenario).T
      content.append(
          SummedBetaPosterior(
          num_success=num_success,
          num_total=num_total,
          kwargs={"linestyle": "--", "label": None},
        )
      )
    draw(
      axes=axes[i,j],
      contents=content,
      xlims=(0., 30. if midext else 10.),
    )
